\documentclass[a4paper]{article}
\usepackage{spconf}
%% \usepackage{geometry}

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}

% \usepackage{fullpage}
% \linespread{1.5}

\usepackage{graphicx, url}
\usepackage{amsmath, amsfonts, xfrac}
\usepackage{mathtools}

\usepackage{multirow}

\usepackage{tikz}
\usetikzlibrary{positioning}

% \usepackage{natbib}

\newcommand{\Real}{\mathbb{R}}
\newcommand{\Cplx}{\mathbb{C}}

\newcommand{\pr}{\mathbb{P}}
\newcommand{\ex}{\mathbb{E}}
\newcommand{\var}{\text{var}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\Ncal}{\mathcal{N}}
\newcommand{\Lcal}{\mathcal{L}}

\newcommand{\defn}{\mathop{\overset{\Delta}{=}}\nolimits}
\newcommand{\lpto}{\mathop{\overset{L^p}{\to}}\nolimits}

\newcommand{\re}{\operatorname{Re}\nolimits}
\newcommand{\im}{\operatorname{Im}\nolimits}

\newcommand{\eng}[1]{\foreignlanguage{english}{#1}}

\newcommand{\rus}[1]{\foreignlanguage{russian}{#1}}
\selectlanguage{english}

\title{Studying Self-similar Processes Using the Crossing Tree}
\author{Nazarov Ivan, \rus{101мНОД(ИССА)}\\
	{\small Supervised by: Decrouez Geoffrey Gerard}}

\begin{document}
\maketitle
\begin{abstract}
The Crossing Tree is a recent tool, created to study scale invariance properties
exhibited by network traffic, financial time-series, and natural phenomena in physics
and biology, such as turbulence, earthquakes and heart beat. It provides an ad-hoc
representation of the data across a wide range of resolutions and independent of
its time scale. In this paper the theoretical and practical construction of the Crossing
Tree is presented. This tool is applied to analyse self-similar signals of processes
known as Hurst self-similar processes with stationary increments to gather evidence 
of the common features of the constructed crossing trees in this class of processes.
\end{abstract}
%% \tableofcontents

%% The project itself
\section{Introduction} % (fold)
\label{sec:introduction}

Scale-invariance and self-similarity has been widely used lately to analyse a wide
range of time series, from medicine, to seismology, and to financial data.
Essentially, scale-invariance of some process implies that its dynamics is not
characterized by well defined dominant time-scales. Instead their dynamics
involve all time-scales. Analysing this kind of data should rely on identifying
the mechanism relating the scales with one another. The crossing tree, described in
section \ref{sec:the_crossing_tree} (p.~\pageref{sec:the_crossing_tree}), is
a natural tool for analysing data at all scales simultaneously.

The structure of this paper is as follows. The second chapter (p.~\pageref{sec:the_crossing_tree})
of this study describes the crossing tree, its theoretical construction as well
as practical computation. In the third chapter we review the definition and classical
examples of self-similar processes with stationary increments (p.~\pageref{sec:h_sssi_processes}).
The last chapter (p.~\pageref{sec:the_crossing_tree_and_h_sssi_processes}) discusses
the results of a Monte-Carlo simulation of crossing trees constricted for sample
paths of various $H$-sssi processes, and attempts verify whether these processes
share common crossing tree statistical properties.

% section introduction (end)

%% Include the contents of the second chapter
%% \clearpage
\include{Chapter2}

%% Include the contents of the third chapter
%% \clearpage
\include{Chapter3}

%% The contents of the fourth chapter
%% \clearpage
\include{Chapter4}

%% Include the conclusions
%% \clearpage
\include{conclusion}

%% End of the report: lists of object and references
% \clearpage \listoffigures
% \clearpage \listoftables

%% \clearpage

\selectlanguage{english}

% \bibliographystyle{amsplain}
% \bibliographystyle{ugost2008ls}
\bibliographystyle{IEEEbib}
\bibliography{literature}

%% Supplementary material
\selectlanguage{english}
\include{appendix}

\end{document}
